---
title: "Untitled"
author: "me"
date: "2024-06-20"
output:
  word_document: default
  html_document: default
---

#1 Print the structure of your dataset

```{r}
library(readxl)
amazon <- read_excel("amazon.xls", n_max = 8)
View(amazon)
str(amazon)

#2 List the variables in your dataset
{r} ls(amazon)

#3 Print the top 15 rows of your dataset
{r} print(amazon[1:15,])

#4 Write a user defined function using any of the variables from the data set
```{r} calculate_mean<-function(discounted_price) {if (is.numeric(amazon[discounted_price])){return(mean(amazon[discounted_price], na.rm=TRUE))}else{return(“the specified column is not numeric”)}} calculate_mean(discounted_price = )

# 5 Use data manipulation techniques and filter rows based on any logical criteria that exist in your dataset.

```{r}
Newfiltered_amazon = as.data.frame(filter(amazon, amazon$rating > 3, amazon$rating_count < 30000))
print(Newfiltered_amazon)

# 6 Identify the dependent & independent variables and use reshaping techniques and create a new data frame by joining those variables from your dataset
{r} dependent_var<-"discounted_price" independent_var<-"actual_price" new_data_frame<-amazon%>% select(dependent_var, all_of(independent_var)) print(new_data_frame)
{r} reshaped_amazon <-new_data_frame %>% gather(key = "discount_percentage", value = "0.65", all_of(dependent_var)) print(reshaped_amazon)
7 Remove missing values in your dataset
{r} cleaned_data<-na.omit(amazon) print(cleaned_data)
8 Identify and remove duplicated data in your dataset
{r} duplicated_amazon= duplicated(amazon) cleaned_data=amazon[!duplicated_amazon,] print(cleaned_data)
9 Reorder multiple rows in descending order
{r} sorted<-amazon %>% arrange(desc(amazon$rating_count), desc(amazon$rating), desc(amazon$discount_percentage)) print(sorted)
10 Rename some of the column names in your dataset
{r} renamed_new = rename(amazon, new_rating=rating, new_rating_count=rating_count) print(renamed_new)
11 Add new variables in your data frame by using a mathematical function (for e.g. – multiply an existing column by 2 and add it as a new variable to your data frame)
{r} reshaped_amazon<-reshaped_amazon%>% mutate(double_0.65=0.65*2) print(reshaped_amazon)
12 Create a training set using random number generator engine
```{r} set.seed(123) train_indices<- sample(seq_len((nrow(amazon))), size = 0.7*nrow(amazon)) train_set <- amazon[train_indices,] test_set <- amazon[-train_indices, ]

# 13 Print the summary statistics of your dataset

```{r}
summary(amazon)
#14 Use any of the numerical variables from the dataset and perform the following statistical functions Mean, median, mode, range
Mean
{r} numeric_variable <-amazon$rating mean_value<-mean(numeric_variable, na.rm = TRUE) mean(numeric_variable      )
Median
{r} median_value <- median(numeric_variable, na.rm = TRUE) median(numeric_variable)
Mode
{r} get_mode <- function(v) {uniq_v <- unique(v) + uniq_v[which.max(tabulate(match(v, uniq_v)))] } mode_value<-get_mode(numeric_variable) print(mode_value)
Range
{r} range_value <- range(numeric_variable, na.rm = TRUE) print(numeric_variable)
15 Plot a scatter plot for any 2 variables in your dataset
{r} ggplot(amazon, aes(x=discounted_price, y=actual_price)) + geom_point() + labs(title = "Scatter Plot", x= "X Axis Label", y="Y Axis Label")
16 Plot a bar plot for any 2 variables in your dataset
{r} ggplot(amazon, aes(x = discounted_price, y = actual_price)) +geom_bar(stat = "identity")
17 Find the correlation between any 2 variables by applying Pearson correlation
```{r} correlation <- cor(amazondiscount_p ercentage,amazondiscount_percentage, method = “pearson”, use = “complete.obs”) cat(“Pearson Correlation:”, correlation, “”)
